Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-08-16 batchdedup/analysis.tex
Updated performance model
Updated batchdedup model

Define $r = s v (1-d_1)/(ck)$  which is the average number of detection
requests made by each machine, and the number of detection requests each
machine must handle.  We assume the load, i.e., amount of data to backup at
each machine, is not balanced, so there is also $r_max$, which is the number of
requests at the most heavily loaded machine. This is the case in the Alibaba
cluster, with some machines being terabytes while the average machine is 40GB.

@@

In Stage 1a, the dirty segments are read from the virtual disk, the hash of
each block is computed, and dedup requests are sent to the machine hosting the
blocks' respective partitions. Due to the synchronization in each stage, Stage
1a needs to wait for the most heavily loaded machine to read all it's data - so
the read stage depends on $r_{max}$, while the write stage, which is balanced
by the hash partitioning, depends on $r$. We first read $r$ blocks from disk,
send $r$ dedup requests, and then save the received requests to temporary files
(one for each parition). The time for the first stage can be expressed as:
\[
    r_{max} c / b_d + \alpha_n\frac{p u r_{max}}{m_n} + r u / b_w
\]

@@

In Stage 2a the new block results from Stage 1 are sent to the requesters, and
in Stage 2b the new blocks are written out to the storage system. We will now
mostly be dealing with the $r(1-d_2)$ blocks that are new to the system (or
$r_{max}(1-d_2)$ when we must wait for the most heavily loaded machine). In 2b
the dedup results must be read and the actual disk blocks for each new block
must be re-read before they can be sent to the block store. The CoW locking on
the filesystem cannot end until after the dirty data is re-read in Stage 2b.

The cost of Stage 2a is:
\[
    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2) p}{m_n} + r_{max}(1-d_2)e / b_w
\]
and the cost of Stage 2b is:
\[
    r_{max}(1-d_2)(e+c) / b_r + r(1-d_2)c / b_b
\]

@@

In the final stage (Stage 4), all duplicate references (including the
dup-with-new references from 3b) are returned to the requesters, so that the
snapshot recipes may be updated with references to those blocks. This process
costs:
\[
    r d_3 e / b_r + \alpha_n\frac{e r_{max} d_3 p}{m_n} + r e / b_w
\]

>>>>

Define $r = s v (1-d_1)/c$  which is the average number of detection
requests made by each machine, and the number of detection requests each
machine must handle.  We assume the load, i.e., amount of data to backup at
each machine, is not balanced, so there is also $r_max$, which is the number of
requests at the most heavily loaded machine. This is the case in the Alibaba
cluster, with some machines being terabytes while the average machine is 40GB.

@@

In Stage 1a, the dirty segments are read from the virtual disk, the hash of
each block is computed, and dedup requests are sent to the machine hosting the
blocks' respective partitions. Due to the synchronization in each stage, Stage
1a needs to wait for the most heavily loaded machine to read all it's data - so
the read stage depends on $r_{max}$, while the write stage, which is balanced
by the hash partitioning, depends on $r$. We first read $r$ blocks from disk,
send $r$ dedup requests, and then save the received requests to temporary files
(one for each parition). The time for the first stage can be expressed as:
\[
    r_{max} c / b_r + \alpha_n\frac{p u r_{max}}{m_n} + r u / b_w
\]

@@

In Stage 2a the new block results from Stage 1 are sent to the requesters, and
in Stage 2b the new blocks are written out to the storage system. We will now
mostly be dealing with the $r(1-d_2)$ blocks that are new to the system (or
$r_{max}(1-d_2)$ when we must wait for the most heavily loaded machine). In 2b
the dedup results must be read and the actual disk blocks for each new block
must be re-read before they can be sent to the block store. To avoid seeking
we have found it faster to simply re-read all the dirty data and ignore the
duplicate blocks rather than find only the new blocks on disk. The CoW locking
on the filesystem cannot end until after the dirty data is re-read in Stage 2b.

The cost of Stage 2a is:
\[
    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2) p}{m_n} + r_{max}(1-d_2)e / b_w
\]
and the cost of Stage 2b is:
\[
    r_{max}c / b_r + r_{max}(1-d_2)e / b_r + r(1-d_2)c / b_b
\]

@@

In the final stage (Stage 4), all duplicate references (including the
dup-with-new references from 3b) are returned to the requesters, so that the
snapshot recipes may be updated with references to those blocks. This process
costs:
\[
    r d_2 e / b_r + \alpha_n\frac{e r_{max} d_2 p}{m_n} + r e / b_w
\]
